### 2021-11-18 response/response.tex

For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}. As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
Therefore we cannot predict the off-diagonal component behavior of the system. However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor. As mentioned in Ref. \cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly agree with  experiment observations
\begin{equation} \tag{1}
  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
\end{equation}
By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system. However, using the dressing field, we can squeeze the conductivity peaks on Landau levels, i.e., squeeze the region of longitudinal conductivity peaks placed near the Landau levels. This  implies sudden Hall conductivity transitions between one plateau to another near a Landau level. As in Refs.  \cite{klitzing80,gusynin06}, we can also predict a staircase behavior of quantum Hall conductivity against the gate voltage. With an external dressing field, we will be able to get rapid transitions than the undressed system. However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the beginning. It will be the subject of our future study.

@@

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

We made the following changes in language and presentation to improve the clarity of our manuscript.

\begin{itemize}
  \item Section VIII (page 8):\\
  {\color{Red}
  Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref. \cite{endo09}. The authors of Ref. \cite{dini16} have used the conventional expression of longitudinal conductivity from Refs. \cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels. These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
  However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
  }
  \item Section III - first paragraph (page 3):\\
  {\color{Red}
  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
  }
  \item Section I - fifth paragraph (page 2):\\
  {\color{Red}
  The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
  }
  \item Section IV - third paragraph (page 5):\\
  {\color{Red}
  In the study presented in Ref. \cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
  }
\end{itemize}

### 2021-11-18 response/response.tex

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

We omitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system. Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well. As mentioned in the work of Endo \textit{et al.} \cite{endo09}, within the magnetic field range of interest, the undressed
magneto-transport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects. Our work is very similar to theirs with an additional dressing field. Our results for the undressed system agree with the results in Ref. \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks. We have added this clarification in the manuscript.

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Red}
  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions. This is not an overly restrictive assumption and others have used the same assumption in their work, e.g. see \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - first paragraph (page 10):\\
  {\color{Red}
  We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
  }
\end{itemize}
